Simulation Results

### 2020-05-03 Simulation Results/Simulation Results.Rmd
tvd update

##

>>>>

## Accuracy benchmarking

```{r}
bugs_fit_condense <- readRDS(here("Simulation Results", "simple-models", 
                                  "discrete", "binomial", "beta-prior", 
                                  "bugs_fit_condense_beta_binomial.RDS"))
jags_fit_condense <- readRDS(here("Simulation Results", "simple-models", 
                                  "discrete", "binomial", "beta-prior", 
                                  "jags_fit_condense_beta_binomial.RDS"))
stan_fit_condense <- readRDS(here("Simulation Results", "simple-models", 
                                  "discrete", "binomial", "beta-prior", 
                                  "stan_fit_condense_beta_binomial.RDS"))
greta_fit_condense <- readRDS(here("Simulation Results", "simple-models", 
                                  "discrete", "binomial", "beta-prior", 
                                  "greta_fit_condense_beta_binomial.RDS"))
nimble_fit_condense <- readRDS(here("Simulation Results", "simple-models", 
                                  "discrete", "binomial", "beta-prior", 
                                  "nimble_fit_condense_beta_binomial.RDS"))
dists <- tibble(
  x = c(bugs_fit_condense, jags_fit_condense, stan_fit_condense, 
        greta_fit_condense, nimble_fit_condense),
  method = c(rep("bugs", length(bugs_fit_condense)),
             rep("jags", length(jags_fit_condense)),
             rep("stan", length(stan_fit_condense)),
             rep("greta", length(greta_fit_condense)),
             rep("nimble", length(nimble_fit_condense))
             )
)

dists %>% 
  ggplot(aes(x, color = method)) + 
  geom_density(adjust = 2) + 
  stat_function(fun = dbeta, args = list(3,9), color = "black")

tibble(x = bugs_fit_condense) %>% 
  ggplot(aes(x)) + 
    geom_density(adjust = 2) + 
    stat_function(fun = dbeta, args = list(3,9), color = "red")

tibble(x = jags_fit_condense) %>% 
  ggplot(aes(x)) + 
    geom_density(adjust = 2) + 
    stat_function(fun = dbeta, args = list(3,9), color = "red")

tibble(x = stan_fit_condense) %>% 
  ggplot(aes(x)) + 
    geom_density(adjust = 2) + 
    stat_function(fun = dbeta, args = list(3,9), color = "red")

```{r}
exp_gamma_acc_files <- c(
  here("Simulation Results", "simple-models", "continuous", "exponential", "gamma-prior", "exponential-gamma-accuracy.rds"),
  here("Simulation Results", "simple-models", "continuous", "exponential", "gamma-prior", "exponential-gamma-accuracy-nimble.rds")
)

normal_gamma_tau_acc_files <- c(
  here("Simulation Results", "simple-models", "continuous", "normal", "gamma-prior-tau", "normal-gamma-tau-accuracy.rds"),
  here("Simulation Results", "simple-models", "continuous", "normal", "gamma-prior-tau", "normal-gamma-tau-accuracy-nimble.rds")
)

normal_normal_acc_files <- c(
  here("Simulation Results", "simple-models", "continuous", "normal", "normal-prior", "normal-normal-accuracy.rds")
  # here("Simulation Results", "simple-models", "continuous", "normal", "normal-prior", "normal-normal-accuracy-nimble.rds")
)

beta_bernoulli_acc_files <- c(
  here("Simulation Results", "simple-models", "discrete", "bernoulli", "beta-prior", "beta-bernoulli-accuracy.rds"),
  here("Simulation Results", "simple-models", "discrete", "bernoulli", "beta-prior", "beta-bernoulli-accuracy-nimble.rds")
)

beta_binomial_acc_files <- c(
  here("Simulation Results", "simple-models", "discrete", "binomial", "beta-prior", "beta-binomial-accuracy.rds"),
  here("Simulation Results", "simple-models", "discrete", "binomial", "beta-prior", "beta-binomial-accuracy-nimble.rds")
)

poisson_gamma_acc_files <- c(
  here("Simulation Results", "simple-models", "discrete", "poisson", "gamma-prior", "poisson-gamma-accuracy.rds"),
  here("Simulation Results", "simple-models", "discrete", "poisson", "gamma-prior", "poisson-gamma-accuracy-nimble.rds")
)

files <- normal_normal_acc_files
model_name <- "poisson_gamma"

combine_time_indiv <- function(files, model_name) {
  combined_results <- files %>% map_dfc(~ readRDS(.)) %>% 
    select(-iter, -iter1) %>% 
    mutate(model = model_name)

  combined_results
}

exp_gamma_acc_df <- exp_gamma_acc_files %>% 
  combine_time_indiv("exponential_gamma")
normal_gamma_tau_acc_df <- normal_gamma_tau_acc_files %>% 
  combine_time_indiv("normal_gamma_tau")
# normal_normal_acc_df <- normal_normal_acc_files %>% 
#   combine_time_indiv("normal_normal")
beta_bernoulli_acc_df <- beta_bernoulli_acc_files %>% 
  combine_time_indiv("beta_bernoulli")
beta_binomial_acc_df <- beta_binomial_acc_files %>% 
  combine_time_indiv("beta_binomial")
poisson_gamma_acc_df <- poisson_gamma_acc_files %>% 
  combine_time_indiv("poisson_gamma")

time_results <- bind_rows(
  exp_gamma_acc_df,
  normal_gamma_tau_acc_df,
  beta_bernoulli_acc_df,
  beta_binomial_acc_df,
  poisson_gamma_acc_df
)

time_results %>% 
  pivot_longer(
    cols = c(jags_dist, bugs_dist, stan_dist, greta_dist, nimble_dist), 
    names_to = "method",
    values_to = "TVD"
  ) %>% 
  ggplot(aes(TVD)) + 
    geom_histogram() + 
    facet_wrap(facets = "method")

time_results %>% 
  pivot_longer(
    cols = c(jags_dist, bugs_dist, stan_dist, greta_dist, nimble_dist), 
    names_to = "method",
    values_to = "TVD"
  ) %>% 
  ggplot(aes(TVD)) + 
    geom_boxplot(aes(color = method)) + 
    coord_flip() + 
    xlim(0,0.25)
